### 2013-11-16 Paper_Markdown.Rmd
Added figure names to the Rmd chunks and started working on the plots.  Moved loading the RData files into data_setup.R.

```{r SiteLocations, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations', echo=FALSE, message=FALSE, warning=FALSE}
map <- map_data('world')

@@

```{r MinMaxDissim, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations', echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r SiteMDS, fig.width=7, fig.height=6, fig.cap='Figure: North American site MDS scores', echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r LoadOutputs, echo=FALSE, message=FALSE, warning=FALSE}
load('data/wa.res.RData')
load('data/mat.res.RData')
load('data/wapls.res.RData')
load('data/rfor.res.RData')
load('data/brt.res.RData')

>>>>

```{r Fig1SiteLocations, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations', echo=FALSE, message=FALSE, warning=FALSE}
map <- map_data('world')

@@

```{r Fig2MinDissim, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations', echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Fig3SiteMDS, fig.width=7, fig.height=6, fig.cap='Figure: North American site MDS scores', echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE}
